---
title: "leaflet RMarkdown"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{leaflet RMarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

I have the following `sf` file of 1000 linestrings (each with an individual id) in `"MULTILINESTRING"` format. 
To visualise the output I've used `tmap` to make a `leaflet` to map the linestrings.  
The output renders fine with `rmarkdown::render()`, but the map won't load when rendered with `pkgdown::build_articles()`


Here's an example with a subset 100 lines which works with both `render()` and `build_articles()`:

```{r setup}
library(tmap)
library(leaflet)
library(sf)
library(rmarkdown)
library(tidyverse)

linestringshp <- readRDS("data/particletracks189.rds") |> slice(1:100)


tmap_mode("view") + 
  tm_shape(linestringshp) + 
  tm_lines()

```

However, I can't get the full 1k lines to run with `build_articles()` - even though `render()` works fine (see below). I don't know if this is a tmap issue or a pkgdown issue (or a poorly generated sf file), but I get the same result using leaflet as with tmap. 
 

```{r}


linestringshp_full <- readRDS("data/particletracks189.rds") 


tmap_mode("view") + 
  tm_shape(linestringshp) + 
  tm_lines()



```

session info:

```{r}

print(sessionInfo())

```
